Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-27 PaperBCJ.tex
cambio final 27 agosto
cambio final 27 agosto

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{array}
\usepackage{filecontents}
%\usepackage[noadjust]{cite}

@@

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}. However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to  introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared(IR) images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
\\

Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use of an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%. Also, another algorithm that uses OTSU and Watershed binarization methods for image segmentation has been developed \cite{hlaing2014weed}. While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally efficient when the weed distribution does not resemble the size of the crop plants, its error increases when crop density is higher compared to weeds. Romeo \textit{et. al} \cite{romeo2012crop} proposed to use a fuzzy clustering approach to correctly segment green within the crop.
\\

>>>>

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage{verbatim}
%\usepackage{array}
%\usepackage{filecontents}
%\usepackage[noadjust]{cite}

@@

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as Precision agriculture(PA)  which has opened a new research field  \cite{ortiz2012máquinas}. However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to  introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by obtaining a set of infrared(IR) images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of weeds in rice crops. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image of plants and performed the crop and weed segmentation with unspecified classifiers.
\\
\\
Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use of an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%. Also, another algorithm that uses OTSU and Watershed binarization methods for image segmentation has been developed \cite{hlaing2014weed}. While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally efficient when the weed distribution does not resemble the size of the crop plants, its error increases when crop density is higher compared to weeds. Romeo \textit{et. al} \cite{romeo2012crop} proposed to use a fuzzy clustering approach to correctly segment green within the crop.
\\
